---
output: 
  pdf_document:
    latex_engine: xelatex
    citation_package: "biblatex"
    template: "./cv-simple.tex"
    md_extensions: "-autolink_bare_uris -auto_identifiers"

name: "Jonathon C. O. Mifsud"

title: "PhD Student"
affiliation: "School of Medical Sciences \\hspace{.05in} \\textbullet \\hspace{.05in} University of Sydney"
contact:
  - text: "jmif9945@uni.sydney.edu.au"
    link: "mailto:jmif9945@uni.sydney.edu.au"
    icon: "Envelope"
    opts: "regular"
    mono: false
  - text: "Website"
    link: "https://jonathonmifsud.github.io"
    icon: "Globe"
    mono: true
  - text: "JonathonMifsud"
    link: "https://github.com/JonathonMifsud"
    icon: "Github"
    mono: true
  - text: "0000-0001-8934-9193"
    link: "https://orcid.org/my-orcid?orcid=0000-0001-8934-9193"
    acad: "Orcid"
    mono: true
    
bibs:
  - "pubbed.bib"
  - "conferences.bib"
  - "inprogress.bib"
  - "review.bib"
  - "press.bib"

namehash: "7ee2eb84ac3fb6ae0cc177587fcaff6a"

raggedright: true

colorlinks: true
linkcolor: "blue"
urlcolor: "magenta"
---

```{r setup, echo = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, comment = "")

library(RefManageR)
library(jtools)
print_refs <- function(file, names = NULL) {
  refs <- ReadBib(file, check = FALSE)
  cat(paste0("\\fullcitebib{", paste(
      c(names(refs) %just% names, names(sort(refs, sorting = "ydnt")) %not% names), 
      collapse = ", "), "}"
    )
  )
}
```

<!-- # Appointments
<!-- 
<!-- ## University of South Carolina \normalfont Columbia, South Carolina, USA
<!-- 
<!-- ### School of Journalism and Mass Communications 
<!-- 
<!-- \vspace{-.05in} 

* Assistant Professor \hfill 2020--
``` -->

# Education

## The University of Sydney \normalfont NSW, Australia

* PhD, School of Medical Sciences \hfill Jun 2021 - Present
  * Supervisor: Edward C. Holmes
  * Co-supervisor: Erin Harvey

## Macquarie University \normalfont NSW, Australia

* Master of Research, Biological Sciences \hfill 2021
  * Thesis: Explorations of the plant virosphere
  * Mark: 92/100
  * Supervisor: Rachael V. Gallagher
  * Co-supervisor: Jemma L. Geoghegan
 

* Bachelor of Advanced Science, Biology \hfill 2018
    

# Grants and Scholarships

\normalfont

Australian Government Research Training Program Stipend, \hfill 2022 - Present
University of Sydney

Postgraduate Research Scholarship in Virus Ecology and Evolution, \hfill 2021-2022
University of Sydney

William Macleay Microbiology Research Fund ($1,500), \hfill 2020

Linnean Society of NSW

RTP Master of Research Stipend, Macquarie University \hfill 2019-2020

# Professional Experience

## Research Assistant
  Phylagen, Inc \normalfont \hfill 2021
  
  Hawkesbury Institute for the Environment, Western Sydney University \normalfont \hfill 2021
  
  GenIMPACT, Macquarie University \normalfont \hfill 2020
  
  Plant Ecology & Conservation Lab, Macquarie University \normalfont \hfill 2019-2020
  
\normalfont

# Presentations 


## Invited talks

Mining RNA viruses across the plant kingdom, Verena Lighthouse  \hfill 2023 \thinspace
  
   Lightning Talk Series (virtual)

## Contributed talks

Identification of a novel papillomavirus from a New Zealand fur seal \hfill 2023 \thinspace

  with oral papilloma-like lesions, MicroSeq  (virtual) 

Transcriptome mining extends the host range of the Flaviviridae \hfill 2022 \thinspace

  to the basal Metazoa, Wellcome Virus Genomics and Evolution 


## Posters

Insights from small scale transcriptome mining projects in Eukaryotes \hfill 2023 \thinspace

  The RdRp Summit (virtual) 

Mining public plant transcriptomes to reveal a diverse plant virosphere \hfill 2020 \thinspace

  Wellcome Genome Infomatics Conference (virtual)

Explorations of the plant virosphere \hfill 2020 \thinspace

  Ecological Society of Australia 60th Anniversary Conference (virtual) 

<!-- # Research in Progress -->

<!-- ```{r results = 'asis'} -->
<!-- print_refs("inprogress.bib", c("long", "longa", "jeonga", "jeong")) -->
<!-- ``` -->


<!-- # Under Review -->

<!-- ```{r results = 'asis'} -->
<!-- print_refs("review.bib",  c("longa", "eveland", "long")) -->
<!-- ``` -->

# Honors and Awards 

Australian Society for Microbiology Award for Best Lightning Talk \hfill 2023 \thinspace 

Executive Dean's Commendation for Academic Excellence in Year 2 MRES \hfill 2021 \thinspace

Year 1 Biology prize for the best MRES Biology student overall \hfill 2019 \thinspace

Macquarie University Merit List \hfill 2019 \thinspace

300 Level Biology Prize for the best student overall \hfill 2018 \thinspace

\normalsize

# Teaching and Service

## Teaching 

Peer Assisted Learning, Macquarie University \hfill 2017-2018 \thinspace 

  \small 
  
  \vspace{-.07in}
  
  BIOL 115: Genes to Organisms
  
  \vspace{-.07in}
  BIOL 122: Biological Basis of Behaviour

\normalsize

## Outreach

\normalsize

Big Picture, Sydney Secondary College, Balmain, NSW, Australia \hfill 2023 \thinspace

## Workshops

Macquarie University R-Users Group Committee \hfill 2020 \thinspace
  \small 
  
  \vspace{-.07in}
  Hosted and presented workshops and help sessions on Introductory R topics

\normalsize

## Journal Reviewing


Archives of Virology  \hfill 2023 \thinspace 
  
<!-- \newpage -->
\normalsize

# Publications

```{r results = 'asis'}
print_refs <- function(file, names = NULL) {
  refs <- ReadBib(file, check = FALSE)
  cat(paste0("\\fullcitebib{", paste(
      c(names(refs) %just% names, names(sort(refs, sorting = "ydnt")) %not% names), 
      collapse = ", "), "}"
    )
  )
}
print_refs("pubbed_no_ann.bib")
```

# Books
```{r results='asis'}
print_refs("books.bib")
```

# Software

BatchArtemisSRAMiner - Virus Discovery Pipeline [Shell and R app]. 

\vspace{-.05in}

* doi:[10.5281/zenodo.8417950](https://doi.org/10.5281/zenodo.8417950)

\small 
\vspace{-.07in}

* \faGithub \hspace{.02in} [github.com/JonathonMifsud/BatchArtemisSRAMiner](https://github.com/JonathonMifsud/BatchArtemisSRAMiner) 


<!-- \pagebreak -->

<!-- # References -->

<!-- \begin{multicols}{2} -->

<!-- \textbf{William P. ``Chip'' Eveland, Jr.} \\ -->
<!-- \textit{Professor of Communication} \\ -->
<!-- \textit{Professor of Political Science (by courtesy)} \\ -->
<!-- School of Communication \\ -->
<!-- The Ohio State University \\  -->
<!-- 3139 Derby Hall \\ -->
<!-- 154 North Oval Mall \\ -->
<!-- Columbus, OH 43210 \\ -->
<!-- \href{mailto:eveland.6@osu.edu}{eveland.6@osu.edu} -->

<!-- \textbf{Gerald M. Kosicki} \\ -->
<!-- \textit{Associate Professor} \\ -->
<!-- \textit{Section Head, Journalism Programs} \\ -->
<!-- School of Communication \\ -->
<!-- The Ohio State University \\  -->
<!-- 3138 Derby Hall \\ -->
<!-- 154 North Oval Mall \\ -->
<!-- Columbus, OH 43210 \\ -->
<!-- \href{mailto:kosicki.1@osu.edu}{kosicki.1@osu.edu} -->

<!-- \columnbreak -->

<!-- \textbf{Michael D. Slater} \\ -->
<!-- \textit{Social and Behavioral Sciences \\ Distinguished Professor \\ -->
<!-- Director}, School of Communication \\ -->
<!-- The Ohio State University \\  -->
<!-- 3022 Derby Hall \\ -->
<!-- 154 North Oval Mall \\ -->
<!-- Columbus, OH 43210 \\ -->
<!-- \href{mailto:slater.59@osu.edu}{slater.59@osu.edu} -->
<!-- \end{multicols} -->
